---
title: "Introduction to ```visualizeBF```"
output: 
  md_document:
    variant: markdown_github
---

The ```visualizeBF``` package is useful for teaching about Bayes Factors, providing two different visual interpretations of the concept.

This is mostly a toy package useful for teaching.

# Installation

You need the ```devtools``` package to install this from github.

```{r, eval=F}
install.packages("devtools")
```

Then install ```visualizeBF```.

```{r, eval=F}
devtools::install_github("mcbeem/visualizeBF")
```

And then load it.

```{r, echo=T, eval=F}
library(visualizeBF)
```

```{r, include=F}
library(visualizeBF)
```


# Example

First, simulate some data.

```{r}
set.seed(1)
data <- rnorm(n=50, mean=.3, sd=1)
```

Visualize the BF as the ratio of the weighted average likelihood under $H_1$ to the likelihood of the data under $H_0$ (via ```plot=1```).

```{r, fig.width=9, fig.height=3}
visualizeBF(data, plot=1)
```

Visualize the BF as the ratio of prior to posterior density under $H_0$ (via ```plot=2```).

```{r, fig.width=9, fig.height=3}
visualizeBF(data, plot=2)
```

